COG-ED Manuscript

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
changed which pipelines will be calculated

  # create new data frames for the specification curve analysis
  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
  #
  # across which dimensions the tranformation and outlier exclusion will be done:
  #   (AA) across subjects, across n-back levels
  #   (AW) across subjects, within n-back levels
  #   (WW) within subjects, within n-back levels
  #   (WA) within subjects, across n-back levels
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 SDs from the mean
  #   (3) 3 SDs from the mean
  #   (T) 0-100 ms after stimulus onset
  # Post-error trials:
  #   (E) excluded
  #   (N) not excluded
  #
  # Example: the data frame "AWL3E" has log-transformed RT data with no data points beyond 3 SD
  # from the mean and with no trials that followed misses/false alarms
  #
  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R___) with either no outlier
  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
  # time-based exclusion is nonsensical for transformed data sets.

@@

  pipelines_data <- replicate(92, data_nback, simplify = FALSE)
  pipelines_data <- setNames(pipelines_data, c("AARNN","AARNE","AAR2N","AAR2E","AAR3N","AAR3E","AARTN","AARTE",
                                               "AALNN","AALNE","AAL2N","AAL2E","AAL3N","AAL3E",
                                               "AAINN","AAINE","AAI2N","AAI2E","AAI3N","AAI3E",
                                               "AASNN","AASNE","AAS2N","AAS2E","AAS3N","AAS3E",
                                               "AWR2N","AWR2E","AWR3N","AWR3E",
                                               "AWLNN","AWLNE","AWL2N","AWL2E","AWL3N","AWL3E",
                                               "AWINN","AWINE","AWI2N","AWI2E","AWI3N","AWI3E",
                                               "AWSNN","AWSNE","AWS2N","AWS2E","AWS3N","AWS3E",
                                               "WWR2N","WWR2E","WWR3N","WWR3E",
                                               "WWLNN","WWLNE","WWL2N","WWL2E","WWL3N","WWL3E",
                                               "WWINN","WWINE","WWI2N","WWI2E","WWI3N","WWI3E",
                                               "WWSNN","WWSNE","WWS2N","WWS2E","WWS3N","WWS3E",
                                               "WAR2N","WAR2E","WAR3N","WAR3E",
                                               "WALNN","WALNE","WAL2N","WAL2E","WAL3N","WAL3E",
                                               "WAINN","WAINE","WAI2N","WAI2E","WAI3N","WAI3E",
                                               "WASNN","WASNE","WAS2N","WAS2E","WAS3N","WAS3E"))

@@

@@

@@

@@

@@

    # the 100-ms-exclusion and the post-error-exclusion are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:

    # exclude RTs fast than 100 ms after stimulus onset if the fourth letter in the data frame name is a "T"
    # also making sure that there are even any trials below 100 ms, otherwise you get an error message

    if (pipeline_name[[1]][4] == "T") {

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])
    }

    # exclude post-error trials if the fifth letter in the data frame name is an "E"
    # also making sure that there are even any error-/post-error-rows left to perform the exclusion, otherwise you get an error message

    if (pipeline_name[[1]][5] == "E") {

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ],
             pipelines_data[[i]] <- pipelines_data[[i]])

    }
  }

>>>>

  # create new data frames for the specification curve analysis
  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
  #
  # across which dimensions the tranformation and outlier exclusion will be done:
  #   (AA) across subjects, across n-back levels
  #   (AW) across subjects, within n-back levels
  #   (WW) within subjects, within n-back levels
  #   (WA) within subjects, across n-back levels
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 MADs from the median
  #   (5) 2.5 MADs from the median
  #   (3) 3 MADs from the median
  #   (O) 0-100 ms after stimulus onset
  #   (T) 0-200 ms after stimulus onset
  #
  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
  # from the median
  #
  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
  # time-based exclusion is nonsensical for transformed data sets.

@@

  pipelines_data <- replicate(63, data_nback, simplify = FALSE)
  pipelines_data <- setNames(pipelines_data, c("AARN","AAR2","AAR5","AAR3","AARO","AART",
                                               "AALN","AAL2","AAL5","AAL3",
                                               "AAIN","AAI2","AAI5","AAI3",
                                               "AASN","AAS2","AAS5","AAS3",
                                               "AWR2","AWR5","AWR3",
                                               "AWLN","AWL2","AWL5","AWL3",
                                               "AWIN","AWI2","AWI5","AWI3",
                                               "AWSN","AWS2","AWS5","AWS3",
                                               "WWR2","WWR5","WWR3",
                                               "WWLN","WWL2","WWL5","WWL3",
                                               "WWIN","WWI2","WWI5","WWI3",
                                               "WWSN","WWS2","WWS5","WWS3",
                                               "WAR2","WAR5","WAR3",
                                               "WALN","WAL2","WAL5","WAL3",
                                               "WAIN","WAI2","WAI5","WAI3",
                                               "WASN","WAS2","WAS5","WAS3"))

@@

          } else if (pipeline_name[[1]][4] == "5") {

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 2.5 * pipemad)
                                                               & pipelines_data[[i]]$rt > (pipemedian - 2.5 * pipemad))), ]
          } else if (pipeline_name[[1]][4] == "3") {

@@

            } else if (pipeline_name[[1]][4] == "5") {

              ifelse(length(which(pipelines_data[[i]]$level == x &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
                                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

            } else if (pipeline_name[[1]][4] == "5") {

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

            } else if (pipeline_name[[1]][4] == "5") {

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

    # the time-based exclusions are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:

    # exclude RTs fast than 100 or 200 ms after stimulus onset if the fourth letter in the data frame name is an "O" or a "T"
    # also making sure that there are even any trials below 100/200 ms, otherwise you get an error message

    if (pipeline_name[[1]][4] == "O") {

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])

    } else if (pipeline_name[[1]][4] == "T") {

      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]) > 0,
             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ],
             pipelines_data[[i]] <- pipelines_data[[i]])
